GM12878 General Read Sequence Figure Generation

### 2022-06-14 R/GM12878DeaminationSequenceAndPositionDataGeneration.rmd
Update cisplatin notebooks
- Support for all_reps
- Read length counting occurs during data generation

expansionOffset = 0
cellType = "GM12878"
CisplatinTimepoints = list(`90min` = NULL)
minReadLength = 22; maxReadLength = 30

@@

```{r read_mismatch_data}
# Get file paths for the mismatch by read data
CisplatinMismatchData = list(rep1 = CisplatinTimepoints,
                             rep2 = CisplatinTimepoints)
for (i in 1:length(CisplatinMismatchData)) {
  for (j in 1:length(CisplatinMismatchData[[i]])) {
    CisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "cisplatin", timepoint = names(CisplatinMismatchData[[i]])[j],
      repitition = names(CisplatinMismatchData)[i], filtering = filtering
      ))
  }
}
```

```{r generate_and_write_simplified_and_filtered_mismatch_data}
# Perform general filtering on the data
CisplatinMismatchData = lapply(CisplatinMismatchData, function(x) lapply(
  x, function(y) filterResults(y, TRUE, 3, minReadLength, maxReadLength)
))

# Simplify the data
CisplatinMismatchData = lapply(CisplatinMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, includeTrinucleotideContext = TRUE)
))

# Write the simplified mismatch data
for (i in 1:length(CisplatinMismatchData)) {
  for (j in 1:length(CisplatinMismatchData[[i]])) {
    fwrite(CisplatinMismatchData[[i]][[j]], sep = '\t', na = "NA",
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
             cellType = cellType, lesion = "cisplatin", timepoint = names(CisplatinMismatchData[[i]])[j],
             repitition = names(CisplatinMismatchData)[i], filtering = filtering
           ))
  }
}
```

```{r generate_and_write_mismatch_frequency_z-scores}
# Don't forget to subset by C>T mismatches!
CisplatinMMFreqZScores = lapply(CisplatinMismatchData, function(x) lapply(
  x, function(y) {
    getMismatchFrequencyZScoreByPosAndReadLength(y[Mismatch == "C>T"], expansionOffset)
  }
))

for (i in seq_along(CisplatinMMFreqZScores)) {
  for (j in seq_along(CisplatinMMFreqZScores[[i]])) {
    fwrite(CisplatinMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinMMFreqZScores)[i],
      timepoint = names(CisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
    ))
  }
}
```

```{r generate_and_write_mismatch_position_statistics_by_read_length_and_timepoint}
CisplatinGroupedStats = list(rep1 = list(), rep2 = list())
CisplatinGroupedStats$rep1$three_prime = getGroupedPositionStats(CisplatinMismatchData$rep1, includedTypes = c("C>T"))
CisplatinGroupedStats$rep2$three_prime = getGroupedPositionStats(CisplatinMismatchData$rep2, includedTypes = c("C>T"))
CisplatinGroupedStats$rep1$five_prime =
  getGroupedPositionStats(CisplatinMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME)
CisplatinGroupedStats$rep2$five_prime =
  getGroupedPositionStats(CisplatinMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME)

for (i in seq_along(CisplatinGroupedStats)) {
  for (j in seq_along(CisplatinGroupedStats[[i]])) {
    fwrite(CisplatinGroupedStats[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
             cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinGroupedStats)[i],
             strandPolarity = names(CisplatinGroupedStats[[i]])[j], filtering = filtering
           ))
  }
}
```

>>>>

expansionOffset = 0
cellType = "GM12878"
cisplatinTimepoints = list(`90min` = NULL)
minReadLength = 22; maxReadLength = 30

@@

```{r read_mismatch_data}
# Get file paths for the mismatch by read data
cisplatinMismatchData = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      mismatchesByReadDirectory, dataTypeStrings$mismatchesByRead, ".bed",
      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
      repitition = names(cisplatinMismatchData)[i], filtering = filtering
      ))
  }
}
```

```{r generate_and_write_simplified_and_filtered_mismatch_data}
# Perform general filtering on the data
cisplatinMismatchData = lapply(cisplatinMismatchData, function(x) lapply(
  x, function(y) filterResults(y, TRUE, 3, minReadLength, maxReadLength)
))

# Simplify the data
cisplatinMismatchData = lapply(cisplatinMismatchData, function(x) lapply(
  x, function(y) simplifyTable(y, includeTrinucleotideContext = TRUE)
))

# Write the simplified mismatch data
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    fwrite(cisplatinMismatchData[[i]][[j]], sep = '\t', na = "NA",
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
             cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
             repitition = names(cisplatinMismatchData)[i], filtering = filtering
           ))
  }
}
```

```{r generate_and_write_mismatch_frequency_z-scores}
# Don't forget to subset by C>T mismatches!
cisplatinMMFreqZScores = lapply(cisplatinMismatchData, function(x) lapply(
  x, function(y) {
    getMismatchFrequencyZScoreByPosAndReadLength(y[Mismatch == "C>T"], expansionOffset)
  }
))

for (i in seq_along(cisplatinMMFreqZScores)) {
  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
    fwrite(cisplatinMMFreqZScores[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
    ))
  }
}
```

```{r generate_and_write_read_length_counts}
cisplatinReadLengthCounts = lapply(cisplatinMismatchData, function(x) lapply(
  x, function(y) {
    y[, .N, by = Read_Length][order(Read_Length)]
  }
))

for (i in seq_along(cisplatinReadLengthCounts)) {
  for (j in seq_along(cisplatinReadLengthCounts[[i]])) {
    fwrite(cisplatinReadLengthCounts[[i]][[j]], sep = '\t', file = generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinReadLengthCounts)[i],
      timepoint = names(cisplatinReadLengthCounts[[i]])[j], filtering = filtering
    ))
  }
}
```

```{r generate_and_write_mismatch_position_statistics_by_read_length_and_timepoint}
cisplatinGroupedStats = list(rep1 = list(), rep2 = list(), all_reps = list())
for (i in seq_along(cisplatinGroupedStats)) {
  cisplatinGroupedStats[[i]]$three_prime = getGroupedPositionStats(cisplatinMismatchData[[i]], includedTypes = c("C>T"))
  cisplatinGroupedStats[[i]]$five_prime =
    getGroupedPositionStats(cisplatinMismatchData[[i]], includedTypes = c("C>T"), posType = FIVE_PRIME)
}

for (i in seq_along(cisplatinGroupedStats)) {
  for (j in seq_along(cisplatinGroupedStats[[i]])) {
    fwrite(cisplatinGroupedStats[[i]][[j]], sep = '\t',
           file = generateFilePath(
             deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
             cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinGroupedStats)[i],
             strandPolarity = names(cisplatinGroupedStats[[i]])[j], filtering = filtering
           ))
  }
}
```

### 2022-06-14 R/GM12878DeaminationSequenceAndPositionFigureGeneration.rmd
Update cisplatin notebooks
- Support for all_reps
- Read length counting occurs during data generation

cellType = "GM12878"
CisplatinTimepoints = list(`90min` = NULL)
minReadLength = 22; maxReadLength = 30

@@

```{r read_simplified_mismatch_data}
# Get file paths for the mismatch by read data
CisplatinMismatchData = list(rep1 = CisplatinTimepoints,
                             rep2 = CisplatinTimepoints)
for (i in seq_along(CisplatinMismatchData)) {
  for (j in seq_along(CisplatinMismatchData[[i]])) {
    CisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "cisplatin", timepoint = names(CisplatinMismatchData[[i]])[j],
      repitition = names(CisplatinMismatchData)[i], filtering = filtering
    ))
  }
}
```

```{r cisplatin_mismatch_type_frequency}
for (i in 1:length(CisplatinMismatchData)) {
  for (j in 1:length(CisplatinMismatchData[[i]])) {
    plotMismatchTypeFrequencies(CisplatinMismatchData[[i]][[j]],
                                title = paste(c("cisplatin", titleCaseFiltering, names(CisplatinMismatchData)[i], 
                                                names(CisplatinMismatchData[[i]])[j], "Mismatch Type Frequency"),
                                              collapse = ' '))
  }
}
```

```{r cisplatin_mismatch_pos_frequency}
for (i in 1:length(CisplatinMismatchData)) {
  for (j in 1:length(CisplatinMismatchData[[i]])) {
    plotMismatchPositionFrequencies(CisplatinMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste(c("cisplatin", titleCaseFiltering, names(CisplatinMismatchData)[i], 
                                                    names(CisplatinMismatchData[[i]])[j], "C>T Mismatch Positions"),
                                                  collapse = ' '))
    plotMismatchPositionFrequencies(CisplatinMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste(c("cisplatin", titleCaseFiltering, names(CisplatinMismatchData)[i], 
                                                    names(CisplatinMismatchData[[i]])[j], "!C>T Mismatch Positions"),
                                                  collapse = ' '))
  }
}
```

```{r cisplatin_trinucleotide_context_analysis}
for (i in 1:length(CisplatinMismatchData)) {
  for (j in 1:length(CisplatinMismatchData[[i]])) {
    plotTrinucleotideContext(CisplatinMismatchData[[i]][[j]], includedTypes = c("C>T"),
                             title = paste(c("cisplatin", titleCaseFiltering, names(CisplatinMismatchData)[i],
                                             names(CisplatinMismatchData[[i]])[j], "C>T Mismatch Trinuc Context"),
                                           collapse = ' '))
  }
}
```

```{r read_mismatch_frequency_z-score_tables}
CisplatinMMFreqZScores = list(rep1 = CisplatinTimepoints, rep2 = CisplatinTimepoints)
for (i in seq_along(CisplatinMMFreqZScores)) {
  for (j in seq_along(CisplatinMMFreqZScores[[i]])) {
    CisplatinMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinMMFreqZScores)[i],
      timepoint = names(CisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
    ))
  }
}
```

```{r cisplatin_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(CisplatinMismatchData$rep1, includedTypes = c("C>T"),
                                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = CisplatinMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(CisplatinMismatchData$rep2, includedTypes = c("C>T"),
                                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = CisplatinMMFreqZScores$rep2)
plotPositionAcrossTimepointAndReadLength(CisplatinMismatchData$rep1, includedTypes = c("C>T"), posType = FIVE_PRIME,
                                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq Rep1"),
                                                       collapse = ' '),
                                         zScoreTables = CisplatinMMFreqZScores$rep1)
plotPositionAcrossTimepointAndReadLength(CisplatinMismatchData$rep2, includedTypes = c("C>T"), posType = FIVE_PRIME,
                                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq Rep2"),
                                                       collapse = ' '),
                                         zScoreTables = CisplatinMMFreqZScores$rep2)
```

```{r cisplatin_read_length_distributions}
plotReadLengthFrequencies(CisplatinMismatchData$rep1,
                          title = paste(c("cisplatin", titleCaseFiltering, "Read Length Freq Rep 1"), collapse = ' '))
plotReadLengthFrequencies(CisplatinMismatchData$rep2,
                          title = paste(c("cisplatin", titleCaseFiltering, "Read Length Freq Rep 2"), collapse = ' '))
```

```{r read_mismatch_position_statistics}
CisplatinGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                             rep2 = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(CisplatinGroupedStats)) {
  for (j in seq_along(CisplatinGroupedStats[[i]])) {
    CisplatinGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinGroupedStats)[i],
      strandPolarity = names(CisplatinGroupedStats[[i]])[j], filtering = filtering
    ))
  }
}
```

```{r cisplatin_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
plotGroupedPositionStats(CisplatinGroupedStats$rep1$three_prime, CisplatinGroupedStats$rep1$five_prime, POS_DIFF,
                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Diff Rep1"), collapse = ' '),
                         xAxisBreaks = c(minReadLength:maxReadLength))
plotGroupedPositionStats(CisplatinGroupedStats$rep2$three_prime, CisplatinGroupedStats$rep2$five_prime, POS_DIFF,
                         title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Diff Rep2"), collapse = ' '),
                         xAxisBreaks = c(minReadLength:maxReadLength))
```

>>>>

cellType = "GM12878"
cisplatinTimepoints = list(`90min` = NULL)
repNames = c("rep1", "rep2", "all_reps")
minReadLength = 22; maxReadLength = 30

@@

```{r read_simplified_mismatch_data}
# Get file paths for the mismatch by read data
cisplatinMismatchData = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
for (i in seq_along(cisplatinMismatchData)) {
  for (j in seq_along(cisplatinMismatchData[[i]])) {
    cisplatinMismatchData[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
      cellType = cellType, lesion = "cisplatin", timepoint = names(cisplatinMismatchData[[i]])[j],
      repitition = names(cisplatinMismatchData)[i], filtering = filtering
    ))
  }
}
```

```{r cisplatin_mismatch_type_frequency}
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    plotMismatchTypeFrequencies(cisplatinMismatchData[[i]][[j]],
                                title = paste(c("cisplatin", titleCaseFiltering, names(cisplatinMismatchData)[i], 
                                                names(cisplatinMismatchData[[i]])[j], "Mismatch Type Frequency"),
                                              collapse = ' '))
  }
}
```

```{r cisplatin_mismatch_pos_frequency}
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    plotMismatchPositionFrequencies(cisplatinMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste(c("cisplatin", titleCaseFiltering, names(cisplatinMismatchData)[i], 
                                                    names(cisplatinMismatchData[[i]])[j], "C>T Mismatch Positions"),
                                                  collapse = ' '))
    plotMismatchPositionFrequencies(cisplatinMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste(c("cisplatin", titleCaseFiltering, names(cisplatinMismatchData)[i], 
                                                    names(cisplatinMismatchData[[i]])[j], "!C>T Mismatch Positions"),
                                                  collapse = ' '))
  }
}
```

```{r cisplatin_trinucleotide_context_analysis}
for (i in 1:length(cisplatinMismatchData)) {
  for (j in 1:length(cisplatinMismatchData[[i]])) {
    plotTrinucleotideContext(cisplatinMismatchData[[i]][[j]], includedTypes = c("C>T"),
                             title = paste(c("cisplatin", titleCaseFiltering, names(cisplatinMismatchData)[i],
                                             names(cisplatinMismatchData[[i]])[j], "C>T Mismatch Trinuc Context"),
                                           collapse = ' '))
  }
}
```

```{r read_mismatch_frequency_z-score_tables}
cisplatinMMFreqZScores = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
for (i in seq_along(cisplatinMMFreqZScores)) {
  for (j in seq_along(cisplatinMMFreqZScores[[i]])) {
    cisplatinMMFreqZScores[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinMMFreqZScores)[i],
      timepoint = names(cisplatinMMFreqZScores[[i]])[j], filtering = filtering, includedMismatches = c("C>T")
    ))
  }
}
```

```{r cisplatin_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
for (i in seq_along(cisplatinMismatchData)) {
  plotPositionAcrossTimepointAndReadLength(cisplatinMismatchData[[i]], includedTypes = c("C>T"),
                                           title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq", repNames[i]),
                                                         collapse = ' '),
                                           zScoreTables = cisplatinMMFreqZScores[[i]])
  plotPositionAcrossTimepointAndReadLength(cisplatinMismatchData[[i]], includedTypes = c("C>T"), posType = FIVE_PRIME,
                                           title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Freq", repNames[i]),
                                                         collapse = ' '),
                                           zScoreTables = cisplatinMMFreqZScores[[i]])
}
```

```{r read_read_length_counts}
cisplatinReadLengthCounts = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
for (i in seq_along(cisplatinReadLengthCounts)) {
  for (j in seq_along(cisplatinReadLengthCounts[[i]])) {
    cisplatinReadLengthCounts[[i]][[j]] = fread(generateFilePath(
      directory = deaminationSequenceAndPositionDataDirectory, dataTypeStrings$readLengthcounts, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinReadLengthCounts)[i],
      timepoint = names(cisplatinReadLengthCounts[[i]])[j], filtering = filtering
    ))
  }
}
```

```{r cisplatin_read_length_distributions}
for (i in seq_along(cisplatinReadLengthCounts)) {
  plotReadLengthFrequencies(cisplatinReadLengthCounts[[i]],
                            title = paste(c("cisplatin", titleCaseFiltering, "Read Length Freq", repNames[i]), collapse = ' '))
}
```

```{r read_mismatch_position_statistics}
cisplatinGroupedStats = list(rep1 = list(three_prime = NULL, five_prime = NULL),
                             rep2 = list(three_prime = NULL, five_prime = NULL),
                             all_reps = list(three_prime = NULL, five_prime = NULL))
for (i in seq_along(cisplatinGroupedStats)) {
  for (j in seq_along(cisplatinGroupedStats[[i]])) {
    cisplatinGroupedStats[[i]][[j]] = fread(generateFilePath(
      deaminationSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(cisplatinGroupedStats)[i],
      strandPolarity = names(cisplatinGroupedStats[[i]])[j], filtering = filtering
    ))
  }
}
```

```{r cisplatin_position_differences_across_read_lengths, fig.width = 9, fig.height = 5}
for (i in seq_along(cisplatinGroupedStats)) {
  plotGroupedPositionStats(cisplatinGroupedStats[[i]]$three_prime, cisplatinGroupedStats[[i]]$five_prime, POS_DIFF,
                           title = paste(c("cisplatin", titleCaseFiltering, "C>T Mismatch Pos Diff", repNames[i]), collapse = ' '),
                           xAxisBreaks = c(minReadLength:maxReadLength))
}
```

### 2022-06-14 R/GM12878GeneralReadSequenceDataGeneration.rmd
Update cisplatin notebooks
- Support for all_reps
- Read length counting occurs during data generation

```{r compute_and_write_cisplatin_sequence_frequency}
for (repitition in c("rep1", "rep2")) {
  for (timepoint in names(CisplatinTimepoints)) {
    singleFileFullAnalysis("cisplatin", repitition, timepoint)
  }
}
```

>>>>

```{r compute_and_write_cisplatin_sequence_frequency}
for (repitition in repNames) {
  for (timepoint in names(cisplatinTimepoints)) {
    singleFileFullAnalysis("cisplatin", repitition, timepoint)
  }
}
```

### 2022-06-14 R/GM12878GeneralReadSequenceFigureGeneration.rmd
Update cisplatin notebooks
- Support for all_reps
- Read length counting occurs during data generation

```{r read_sequence_frequencies}
CisplatinTGGSeqFreq = list(rep1 = CisplatinTimepoints, rep2 = CisplatinTimepoints)
for (i in seq_along(CisplatinTGGSeqFreq)) {
  for (j in seq_along(CisplatinTGGSeqFreq[[i]])) {
    CisplatinTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinTGGSeqFreq)[i],
      timepoint = names(CisplatinTGGSeqFreq[[i]])[j], sequence = "TGG"
    ))
  }
}

CisplatinCGASeqFreq = list(rep1 = CisplatinTimepoints, rep2 = CisplatinTimepoints)
for (i in seq_along(CisplatinCGASeqFreq)) {
  for (j in seq_along(CisplatinCGASeqFreq[[i]])) {
    CisplatinCGASeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(CisplatinCGASeqFreq)[i],
      timepoint = names(CisplatinCGASeqFreq[[i]])[j], sequence = "CGA"
    ))
  }
}
```

```{r cisplatin_sequence_frequencies, fig.width = 11, fig.height = 10}
plotSequenceFrequencies(CisplatinTGGSeqFreq$rep1,
                        title = "cisplatin TGG Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))
plotSequenceFrequencies(CisplatinTGGSeqFreq$rep2,
                        title = "cisplatin TGG Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))

plotSequenceFrequencies(CisplatinCGASeqFreq$rep1,
                        title = "cisplatin CGA Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
plotSequenceFrequencies(CisplatinCGASeqFreq$rep2,
                        title = "cisplatin CGA Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("CGA"))
```

@@

```{r cisplatin_read_length_frequencies}
readAndPlotReadLengthFrequencies("cisplatin", "rep1", CisplatinTimepoints)
readAndPlotReadLengthFrequencies("cisplatin", "rep2", CisplatinTimepoints)
```

>>>>

```{r read_sequence_frequencies}
CPDTGGSeqFreq = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
for (i in seq_along(CPDTGGSeqFreq)) {
  for (j in seq_along(CPDTGGSeqFreq[[i]])) {
    CPDTGGSeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(CPDTGGSeqFreq)[i],
      timepoint = names(CPDTGGSeqFreq[[i]])[j], sequence = "TGG"
    ))
  }
}

CPDCGASeqFreq = list(rep1 = cisplatinTimepoints, rep2 = cisplatinTimepoints, all_reps = cisplatinTimepoints)
for (i in seq_along(CPDCGASeqFreq)) {
  for (j in seq_along(CPDCGASeqFreq[[i]])) {
    CPDCGASeqFreq[[i]][[j]] = fread(generateFilePath(
      directory = generalReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = "cisplatin", repitition = names(CPDCGASeqFreq)[i],
      timepoint = names(CPDCGASeqFreq[[i]])[j], sequence = "CGA"
    ))
  }
}
```

```{r cisplatin_sequence_frequencies, fig.width = 11, fig.height = 10}
for (i in seq_along(CPDTGGSeqFreq)) {
  plotSequenceFrequencies(CPDTGGSeqFreq[[i]],
                          title = paste("Cisplatin TGG Frequencies", repNames[i]),
                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
                          showFivePrimeCutSite = TRUE, querySequences = c("TGG"))
}

for (i in seq_along(CPDCGASeqFreq)) {
  plotSequenceFrequencies(CPDCGASeqFreq[[i]],
                          title = paste("Cisplatin CGA Frequencies", repNames[i]), expansionOffset = expansionOffset,
                          showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                          querySequences = c("CGA"))
}
```

@@

```{r cisplatin_read_length_frequencies}
for (rep in repNames) {
  readAndPlotReadLengthFrequencies("cisplatin", rep, cisplatinTimepoints)
}
```
